Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-07 docs/evol.tex
minor fixes

Contrary to the above, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analysing the project's
Bugzilla. Their research showed that security bugs require more experienced developers
to be fixed. In addition, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years.

@@

Our primary expectation was that security bugs and especially severe
ones, should be corrected as projects evolve. But our findigs indicate that this is
not true. Concerning bug persistence, we saw that the behaviour of security
bugs is similar to the other categories. We have to point out the fact that
having an average of two to three versions persistence in a sample where 60\%
of the projects have three versions, is not a positive result especially in the
case of the {\it Security High} bugs. An interesting observation was that
the relation between severe security bugs and a project's size the is different
than the other categories. In essense, a severe bug is introduced only when code
that deals with untrusted input is added in a application. Furthermore, the
pairwise correlations between all categories indicated that severe bugs are
coming from a special kind of carelessness. Finally, it is interesting to see
that security bugs were one of the top two bug categories existing in such a
large ecosystem.

>>>>

Contrary to the above, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analysing the project's
Bugzilla. Their research presented evidence that security bugs require more experienced developers
to be fixed. In addition, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years.

@@

Our primary hypothesis was that security bugs and especially severe
ones, should be corrected as projects evolve. But our findigs indicate that this is
not true. Concerning bug persistence, we saw that the behaviour of security
bugs is similar to the other categories. We have to point out the fact that
having an average of two to three versions persistence in a sample where 60\%
of the projects have three versions, is not a positive result especially in the
case of the {\it Security High} bugs. An interesting observation was that
the relation between severe security bugs and a project's size is different
than the other categories. In essense, a severe bug is introduced only when code
that deals with untrusted input is added in a application. Furthermore, the
pairwise correlations between all categories indicated that severe bugs are
coming from a special kind of carelessness. Finally, it is interesting to see
that security bugs were one of the top two bug categories existing in such a
large ecosystem.
